Copulas reveal complex and informative dependencies propagating throughout ecology

### 2019-05-16 Paper.Rmd
updated length stats
reading as csv

```{r read_somedata, echo=F, results='hide'}
d_soilCN<-readRDS("Data/dataForShymolinaCoord.rds")
d_soilCN<-na.omit(d_soilCN)
d_birdsBMR<-readRDS("./Data/BMR/BirdBodyMassesMetabolicRates/my_birdsBMR_data.RDS")
d_mammalsBMR<-readRDS("./Data/BMR/MammalianBodyMassesMetabolicRates/my_mammalsBMR_data.RDS")
d_cc<-readRDS("./Results/Ceder_creek_results/cop_HB_all_yr.RDS")
```

>>>>

```{r read_somedata, echo=F, results='hide'}
d_soilCN<-read.csv("./Data/SoilCN/SoilCNdata.csv")
rownames(d_soilCN)<-d_soilCN$X
d_soilCN<-d_soilCN[,-1]
d_soilCN<-na.omit(d_soilCN)
d_birdsBMR<-readRDS("./Data/BMR/BirdBodyMassesMetabolicRates/my_birdsBMR_data.RDS")
d_mammalsBMR<-readRDS("./Data/BMR/MammalianBodyMassesMetabolicRates/my_mammalsBMR_data.RDS")
d_cc<-readRDS("./Results/Ceder_creek_results/cop_HB_all_yr.RDS")
```
